Moral Foundations of U.S. Political News Organizations

### 2019-04-06 pilot_manuscript.Rmd
not really making any progress

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F)
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")

@@

```{r data_clean_gs, eval = T, echo = F}
##combine all gs data into one dataset
#read it in
NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F)
NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F)
SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F)
HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F)
POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F)
FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F)
BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F)
RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F)
BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F)
HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F)

>>>>

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #not ok fix
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok

@@

```{r data_clean_gs, eval = T, echo = F}
##combine all gs data into one dataset
#read it in
NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
